### 2009-04-14 docs/runtime_parameters/runtime_parameters.tex
replaced the shell script with a python script that will read in from fParallel/MAESTRO/_parameters and dump out the LaTeX formatted table for use in documentation.
comments within the _parameters file should begin with a "#" symbol and
should be LaTeX friendly (e.g. "$\le$" instead of "<=").

there should also be a space between the header info in _parameters and the
first parameter:

# This file contains...
# .
# .
# .
# file in the problem directory.

# This is used to specify the model file to map into multidimensions
model_file                          character          "model.hse"

etc.

\verb=  beta_type =  & what type of coefficient to use inside the velocity divergence constraint.  
                           {\tt beta\_type} = 1 uses $\beta_0$; {\tt beta\_type} = 2 uses $\rho_0$ (anelastic);
                           {\tt beta\_type} = 3 uses 1 (small-scale combustion).  &  1 \\

@@

\verb=  cg_verbose =  & Verbosity of bottom solver.  &  0 \\

@@

\verb=  co_latitude =  & latitude, in radians, for problems with rotation where the domain is only a subset
                             of a full star.  &  ZERO \\

@@

\verb=  do_eos_h_above_cutoff =  & After the advective enthalpy update, recompute the enthalpy if we are 
                                         below the base cutoff density.   &  .true. \\
\verb=  do_initial_projection =  & Do the initial projection.  & 1 \\

@@

\verb=  enthalpy_pred_type =  & predict\_rhohprime = 1; predict\_h = 2; predict\_T\_then\_rhohprime = 3;
                                      predict\_T\_then\_h = 4; predict\_hprime = 5; predict\_Tprime\_then\_h = 6;
                                    &  predict\_rhohprime \\

@@

\verb=  hg_bottom_solver =  &   &  -1 \\
\verb=  hg_dense_stencil =  & In hgproject, 
                                   In 2D, use a 9 point Laplacian (.true.) or 5-point Laplacian (.false.).
                                   In 3D, use a 27 point Laplacian (.true.) or 7-point Laplacian (.false.). &  .true. \\

@@

\verb=  init_shrink =  & the multiplicative factor ($\le 1$) to reduce the initial timestep as computed by the 
                             various timestep estimators   &  1.0 \\
\verb=  interp_type_radial_bin_to_cart =  & The interpolation for filling a full multifab from a 1D 
                                                     bin-centered array.  1 = piecewise constant; 
                                                     2 = piecewise linear.  &  1 \\

@@

\verb=  lUsingNFiles =  & If .true., use nOutFiles processors to write checkpoint and plotfiles.  
                              Fortran has the unfortunate feature of each processor only being able to write out 
                              1-2GB each without crashing.  &  .true. \\
\verb=  max_dt_growth =  & The maximum scale factor that the time step is allowed to grow by per time step.  
                              &  1.1D0 \\

@@

\verb=  mg_bottom_solver =  &   &  -1 \\

@@

\verb=  model_file =  &   & ``model.hse'' \\
\verb=  n_cellx =  & Number of cells for the base level in the x-direction  &  \\
\verb=  n_celly =  & Number of cells for the base level in the y-direction  &  \\
\verb=  n_cellz =  & Number of cells for the base level in the z-direction  &  \\
\verb=  nOutFiles =  & If lUsingNFiles = .true., use this many processors to write checkpoint and plotfiles.  
                           Fortran has the unfortunate feature of each processor only being able to write out 
                           1-2GB each without crashing.  & 64 \\

@@

\verb=  ppm_type =  &   &  0 \\
\verb=  prob_hi_x =  &   &  \\
\verb=  prob_hi_y =  &   &  \\
\verb=  prob_hi_z =  &   &  \\

@@

\verb=  radius =  &   &  1.0e6 \\

@@

\verb=  temp_diffusion_formulation =  &   &  .false. \\
\verb=  test_set =  &   &  '' \\
\verb=  the_copy_cache_max =  &   & 50 \\
\verb=  the_knapsack_verbosity =  &   &  .false. \\

@@

\verb=  thermal_diffusion_type =  &   &  1 \\
\verb=  the_sfc_threshold =  &   & 5 \\

@@

\verb=  use_divu_firstdt =  &   &  .false. \\
\verb=  use_eos_coulomb =  &   &  .false. \\

@@

\verb=  use_soundspeed_firstdt =  &   &  .false. \\
\verb=  use_tfromp =  &   &  .false. \\
\verb=  use_thermal_diffusion =  &   &  .false. \\
\verb=  velpert_amplitude =  &   &  0.d0 \\
\verb=  velpert_radius =  &   &  0.75d8 \\
\verb=  velpert_scale =  &   &  0.8d8 \\
\verb=  velpert_steep =  &   &  1.d0 \\
\verb=  verbose =  &   &  0 \\
\verb=  w0mac_interp_type =  &   &  1 \\
\verb=  xrb_pert_factor =  &   &  1.d-2 \\
\verb=  xrb_pert_size =  &   &  5.0d1 \\
\verb=  xrb_pert_type =  &   &  1 \\
\verb=  xrb_use_bottom_sponge =  &   &  .true. \\

>>>>

\verb=  beta_type  = &   what type of coefficient to use inside the velocity divergence constraint. {\tt beta\_type} = 1 uses $\beta_0$; {\tt beta\_type} = 2 uses $\rho_0$ (anelastic); {\tt beta\_type} = 3 uses 1 (small-scale combustion).  &  1 \\

@@

\verb=  cg_verbose  = &   Verbosity of bottom solver  &  0 \\

@@

\verb=  co_latitude  = &   latitude, in radians, for problems with rotation where the domain is only a subset of a full star.  &  ZERO \\

@@

\verb=  do_eos_h_above_cutoff  = &   After the advective enthalpy update, recompute the enthalpy if we are below the base cutoff density.  &  .true. \\
\verb=  do_initial_projection  = &   Do the initial projection.  &  .true. \\

@@

\verb=  enthalpy_pred_type  = &   predict\_rhohprime = 1; predict\_h = 2; predict\_T\_then\_rhohprime = 3; predict\_T\_then\_h = 4; predict\_hprime = 5; predict\_Tprime\_then\_h = 6.  &  predict\_rhohprime \\

@@

\verb=  hg_bottom_solver  = &   valid values are $\le$ 0  &  -1 \\
\verb=  hg_dense_stencil  = &   In hgproject, in 2D, use a 9 point Laplacian (.true.) or 5-point Laplacian (.false.).  In 3D, use a 27 point Laplacian (.true.) or 7-point Laplacian (.false.).  &  .true. \\

@@

\verb=  init_shrink  = &   the multiplicative factor ($\le 1$) to reduce the initial timestep as computed by the various timestep estimators  &  1.0 \\
\verb=  interp_type_radial_bin_to_cart  = &   The interpolation for filling a full multifab from a 1D bin-centered array. 1 = piecewise constant; 2 = piecewise linear.  &  1 \\

@@

\verb=  lUsingNFiles  = &   If .true., use nOutFiles processors to write checkpoint and plotfiles. Fortran has the unfortunate feature of each processor only being able to write out 1-2GB each without crashing.  &  .true. \\
\verb=  max_dt_growth  = &   The maximum scale factor that the time step is allowed to grow by per time step.  &  1.1D0 \\

@@

\verb=  mg_bottom_solver  = &   valid values are $\le$ 0  &  -1 \\

@@

\verb=  model_file  = &    &  "model.hse" \\
\verb=  nOutFiles  = &   If lUsingNFiles = .true., use this many processors to write checkpoint and plotfiles.  Fortran has the unfortunate feature of each processor only being able to write out 1-2GB each without crashing.  &  64 \\
\verb=  n_cellx  = &   Number of cells for the base level in the x-direction  &  -1 \\
\verb=  n_celly  = &   Number of cells for the base level in the y-direction  &  -1 \\
\verb=  n_cellz  = &   Number of cells for the base level in the z-direction  &  -1 \\

@@

\verb=  ppm_type  = &   0 = no ppm 1 = 1985 ppm 2 = 2009 ppm  &  0 \\
\verb=  prob_hi_x  = &    &  1.0 \\
\verb=  prob_hi_y  = &    &  1.0 \\
\verb=  prob_hi_z  = &    &  1.0 \\

@@

\verb=  radius  = &    &  1.0e6\_dp\_t \\

@@

\verb=  temp_diffusion_formulation  = &   How to compute the explicit thermal diffusion term. .true. = in terms of $T$; .false. = in terms of $\rho,p_0,X$.  &  .false. \\
\verb=  test_set  = &   Fixed grid file.  &  '' \\
\verb=  the_copy_cache_max  = &    Number of boxassoc layouts we keep in memory to avoid having to recompute the boxassoc, which is computationally expensive.  &  50 \\
\verb=  the_knapsack_verbosity  = &   Verbosity of the knapscak processor-to-grid algorithm.  &  .false. \\

@@

\verb=  the_sfc_threshold  = &   When assigning processors for grids, this determines whether we use the sfc algorithm or knapsack algorithm.  If the total number of grids divided by the number of processors is greater than this number, use sfc.  &  5 \\
\verb=  thermal_diffusion_type  = &   In the thermal diffusion solver, 1 = Crank-Nicholson; 2 = Backward Euler.  &  1 \\

@@

\verb=  use_divu_firstdt  = &   Use the divu constraint when computing the first time step.  &  .false. \\
\verb=  use_eos_coulomb  = &    &  .true. \\

@@

\verb=  use_soundspeed_firstdt  = &   Use the soundspeed constraint when computing the first time step.  &  .false. \\
\verb=  use_tfromp  = &   When updating temperature, use $T=T(\rho,p_0,X) $ rather than $T=T(\rho,h,X)$.  &  .false. \\
\verb=  use_thermal_diffusion  = &   Use thermal diffusion.  &  .false. \\
\verb=  verbose  = &   General verbosity  &  0 \\
\verb=  w0mac_interp_type  = &   0 = Compute w0 at edges using a projection; 1 = Interpolate w0 to cell centers, then average to edges; 2 = Interpolate w0 to edges directly; 3 = Interpolate w0 to nodes, then average to edges.  &  1 \\
